In this section, we summarize requirements that were discussed during development and assigned a \textbf{Priority 5 (Future)}. These items are considered valuable enhancements to \textbf{The Vacu-arm} system but are outside the scope of the current prototype due to constraints such as time, budget, or technical limitations. The items listed here are duplicates of entries from Sections 3 through 8.

\subsection{Advanced Voice and Gesture Control Interface}
\subsubsection{Description}
The system will support real-time voice and hand gesture control to allow for contactless operation of the Vacu-arm. Operators will be able to speak commands or use predefined gestures (e.g., closed fist to grip, open hand to release) recognized by a depth-sensing camera.
\subsubsection{Source}
User feedback; industrial control trends; educational goals
\subsubsection{Constraints}
Accurate speech and gesture recognition requires robust AI models and error handling to prevent unsafe actions.
\subsubsection{Standards}
ISO 10218-1 and ISO 10218-2 (Industrial robot safety) \\
ISO/TS 15066 (Collaborative robot safety)
\subsubsection{Priority}
Future

\subsection{Mobile Power Integration}
\subsubsection{Description}
Future versions of the Vacu-arm may include a battery pack or portable power supply to support mobile or off-grid operation.
\subsubsection{Source}
Team roadmap; mobile use case exploration
\subsubsection{Constraints}
Battery weight, safety, and power capacity must be balanced for real-world tasks.
\subsubsection{Standards}
IEC 61960 (Battery performance testing) \\
ISO 26262 (Functional safety for electrical/electronic systems)
\subsubsection{Priority}
Future

\subsection{Remote Web Interface for Monitoring}
\subsubsection{Description}
The system may include a remote-access dashboard for monitoring Vacu-arm task performance, system health, and video feeds via browser.
\subsubsection{Source}
Future system extensibility planning
\subsubsection{Constraints}
Requires secure IP-based access, user authentication, and live data streaming support.
\subsubsection{Standards}
OWASP Web Security Standards \\
ISO/IEC 27001 (Information Security Management)
\subsubsection{Priority}
Future
