This section describes how the final system will be packaged and presented to the end-user upon delivery. Packaging includes both the physical form factor of hardware components and the distribution method for software components. As this product is intended for general industrial use, it will be designed for ease of deployment, setup, and maintenance by manufacturing engineers or automation specialists. The packaging must ensure protection of sensitive components, compliance with industrial aesthetics and safety standards, and ease of installation. Where applicable, branding, labeling, and user documentation must be included. These packaging requirements are distinct from operational or functional requirements and are focused solely on the product's final physical and distributable form.

\subsection{Requirement Name}
\subsubsection{Description}
A touchscreen or monitor-like display will be physically mounted in close proximity to the UR20 robotic arm to provide real-time system feedback, control status, and manual override capabilities. This monitor will serve as the primary human-machine interface (HMI) and must be designed for both ease of visibility and industrial durability.
\subsubsection{Source}
UR20 arm manufacturing, instructor
\subsubsection{Constraints}
Operator Safety:
The mounting system must ensure the monitor remains securely fastened under vibration, movement, or accidental bumps. Loose or improperly mounted displays could fall or swing into an operator, posing injury risks.
\subsubsection{Standards}
ISO 10218-2:2011 (Robots and Robotic Devices)
\subsubsection{Priority}
Moderate